Kepler's Demographic Cliff: Ages of Young Stars and Planets in the Kepler Field

### 2024-04-27 paper/ms.tex
update ms

%\title{Gyrochrone and Lithium Ages for Stars and Planets Observed by Kepler}
%Ages of the Kepler Stars and Planets
\title{A Dearth of Young Stars and Planets in the Kepler Field}

@@

\begin{figure*}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=\textwidth]{hist_samples_koi_gyro_ages_hist_field_gyro_ages_20240405_maxage3200.pdf}
	\end{center}
	\vspace{-0.6cm}
	\caption{
		{\bf Age distribution of stars (left) and planet hosts
			(right) in the Kepler field inferred from rotation periods}.
		The
		light gray histogram does not impose any requires on factors such as
		binarity, crowding, or the star's evolutionary state;
		the age calculation was more likely to be valid for stars that meet the criteria
		discussed in Section~\ref{subsec:flags} (black).
		\label{fig:hist_tgyro}
	}
\end{figure*}

>>>>

%\title{Gyrochrone and Lithium Ages for Stars and Planets Observed by Kepler}
%Ages of the Kepler Stars and Planets
%\title{A Dearth of Young Stars and Planets in the Kepler Field}
\title{Kepler's Demographic Cliff: Ages of Young Stars and Planets in the Kepler Field}

@@

\begin{figure*}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=\textwidth]{hist_samples_koi_gyro_ages_hist_field_gyro_ages_20240405_maxage3200.pdf}
	\end{center}
	\vspace{-0.6cm}
	\caption{
		{\bf Kepler's demographic cliff,} visible in the
		rotation-derived age distribution of stars (left) and planet hosts
		(right) in the Kepler field.
		The
		light gray histogram does not impose any requires on factors such as
		binarity, crowding, or the star's evolutionary state;
		the age calculation was more likely to be valid for stars that meet the criteria
		discussed in Section~\ref{subsec:flags} (black).
		\label{fig:hist_tgyro}
	}
\end{figure*}
